### 2016-05-31 capability-machine.tex
typos

\[
\stdvr \; : \;  \Worlds \monfun \UPred{\Words}
\]
\begin{align*}
  \stdvr(W) \defeq & \{ \npair{i} \mid i \in \ints \} 
00

@@

Consider what the ``good observations'' should be? Before we do that - what should the end result of a computation be?
\begin{align*}
  \observations \quad : & \quad  \Worlds \monfun \UPred{\Confs} \\
  \observations (W) \defeq & \{ \npair{(\reg,\heap)} \mid \\
                           & \quad (\exists \reg', \heap' \ldotp (\reg,\heap) \step[n] (\reg',\heap')) \lor \\ %Define the step stuff 
                           & \quad (\exists \reg', \heap', i \leq n \ldotp (\reg,\heap) \step[i] \failed) \lor \\
                           & \quad (\forall \heap', i \leq n \ldotp (\reg,\heap) \step[i] (\halted,\heap)  \\
                           & \qquad \Rightarrow \npair[n-1]{\heap(0)} \in \stdvr(W) \land \\
                           & \qquad \qquad \forall r \ldotp 0 \in \dom(W(r)) \ldotp \npair[n-i]{\heap(0)} \in W(r)(W) )\}
\end{align*}
The ``good observations'' are as follows
\begin{itemize}
\item The execution does not stop in $n$ steps. 
\item The execution stops with a $\failed$.
\item The execution halts in at most $n$ steps with a valid value in in address 0 and the value at address 0 is also valid with respect to the world.
\end{itemize}
Address 0 is the designated I/O address.

``Continuation'' relation:
\begin{align*}
  \stdkr \quad : & \quad  \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stdkr(W) \defeq & \{ \npair{c} \mid \\
                   & \quad \forall v\ldotp \in \stdvr(W) \Rightarrow \\
                   & \qquad  \forall W' \future W\ldotp %on the whiteboard, we had public future world.
                     \forall \heapSat[\heap]{n'}{W'}, \npair{v_1 \dots v_k} \in \stdvr(W') \ldotp \\
                   & \qquad \quad (n,[\pcreg \mapsto \updatePcPerm{c},r_0 \mapsto v,r_1 \mapsto v_1,\dots, r_k \mapsto v_k], \heap) \in \observations(W) \}
\end{align*}
``Expression'' relation:
\begin{align*}
  \stder \quad : & \quad \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stder(W) \defeq & \{ \npair{\reg} \mid \\
                   & \quad \forall \npair{c} \in \stdkr(W) \ldotp \\
                   & \qquad  \forall \heapSat[\heap]{n}{W}, \heap_f \ldotp \\
                   & \qquad \quad (n,\reg\update{r_0}{c},\heap \uplus \heap_f) \in \observations(W) \}
\end{align*}
Register-file relation:
\begin{align*}
  \stdgr \quad : & \quad \Worlds \monfun \UPred{\Regs} \\
  \stdgr(W) \defeq & \{ \npair{\reg} \mid \\
                    & \quad \forall r \in \RegName \ldotp \\
                    & \qquad  \npair{\reg(r)} \in \stdvr(W) \}
\end{align*}

>>>>

\stdvr \; : \;  \Worlds \monfun \UPred{\Words}
  \stdvr(W) \defeq & \{ \npair{i} \mid i \in \ints \} 

@@

Consider what the ``good observations'' should be? Before we do that - what should the end result of a computation be?
\begin{align*}
  \observations \quad : & \quad  \Worlds \monfun \UPred{\Confs} \\
  \observations (W) \defeq & \{ \npair{(\reg,\heap)} \mid \\
                           & \quad (\exists \reg', \heap' \ldotp (\reg,\heap) \step[n] (\reg',\heap')) \lor \\ %Define the step stuff 
                           & \quad (\exists \reg', \heap', i \leq n \ldotp (\reg,\heap) \step[i] \failed) \lor \\
                           & \quad (\forall \heap', i \leq n \ldotp (\reg,\heap) \step[i] (\halted,\heap)  \\
                           & \qquad \Rightarrow \npair[n-i]{\heap(0)} \in \stdvr(W) \land \\
                           & \qquad \qquad \forall r \ldotp 0 \in \dom(W(r)) \ldotp \npair[n-i]{\heap(0)} \in W(r)(W) )\}
\end{align*}
The ``good observations'' are as follows
\begin{itemize}
\item The execution does not stop in $n$ steps. 
\item The execution stops with a $\failed$.
\item The execution halts in at most $n$ steps with a valid value in in address 0 and the value at address 0 is also valid with respect to the world.
\end{itemize}
Address 0 is the designated I/O address.

``Continuation'' relation:
\begin{align*}
  \stdkr \quad : & \quad  \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stdkr(W) \defeq & \{ \npair{c} \mid \\
                   & \quad \forall v \in \stdvr(W)\ldotp \\
                   & \qquad  \forall W' \future W\ldotp %on the whiteboard, we had public future world.
                     \forall \heapSat[\heap]{n'}{W'}, \npair{v_1 \dots v_k} \in \stdvr(W') \ldotp \\
                   & \qquad \quad (n,[\pcreg \mapsto \updatePcPerm{c},r_0 \mapsto v,r_1 \mapsto v_1,\dots, r_k \mapsto v_k], \heap) \in \observations(W) \}
\end{align*}
``Expression'' relation:
\begin{align*}
  \stder \quad : & \quad \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stder(W) \defeq & \{ \npair{\reg} \mid \\
                   & \quad \forall \npair{c} \in \stdkr(W) \ldotp \\
                   & \qquad  \forall \heapSat[\heap]{n}{W}, \heap_f \ldotp \\
                   & \qquad \quad (n,\reg\update{r_0}{c},\heap \uplus \heap_f) \in \observations(W) \}
\end{align*}
Register-file relation:
\begin{align*}
  \stdgr \quad : & \quad \Worlds \monfun \UPred{\Regs} \\
  \stdgr(W) \defeq & \{ \npair{\reg} \mid \\
                    & \quad \forall r \in \RegName \ldotp \\
                    & \qquad  \npair{\reg(r)} \in \stdvr(W) \}
\end{align*}
